Prognostic and biological relevance of collagen-related genes in prostate cancer

### 2024-01-23 report/markdown/manuscript_figures_tables.Rmd
Minor update of the figures and tables

---
title: "Prognostic and biological relevance of collagen biosynthesis pathway in prostate cancer"
subtitle: "Methods, figures and tables for the transcriptome part"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

>>>>

---
title: "Prognostic and biological relevance of collagen-related genes in prostate cancer"
subtitle: "Methods, figures and tables for the transcriptome part"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

### 2024-01-23 report/markdown/manuscript_supplement.Rmd
Minor update of the figures and tables

---
title: "Prognostic and biological relevance of collagen biosynthesis pathway in prostate cancer"
subtitle: "Supplementary material, transcriptome part"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

>>>>

---
title: "Prognostic and biological relevance of collagen-related genes in prostate cancer"
subtitle: "Supplementary material, transcriptome part"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
